Verifying Demonstrations

### 2019-06-28 paper/DB-anon-cred.tex
Improves section titles with \acl*
Changes the DB-Schnorr to use k challenges instead of two

\section{Distance-bounding \aclp{ZKPK} for discrete logarithms}%
\label{DB-anon-cred}

@@

    \(s_0\gets \rho - c_0\alpha \pmod q\)
    & \(\ProtoSendLeft{c_0, c_1}\)
    & \(c_0\rgets \bin^k, c_1\rgets \bin^k\)
    \\

    \(s_1\gets \rho - c_1\alpha \pmod q\)
    &
    &
    \\

@@

    % null
    & \(\ProtoSendLeft{b}\)
    & \(b\rgets \bin\)
    \\

    Fetch \(s_b\)
    & \(\ProtoSendRight{s_b}\)
    & Record \(\Delta t\)
    \\

@@

    % null
    &
    & Accept if \(R = g^{s_b} A^{c_b}\).
    \\

  \end{tabular}
  \caption{%
    One-round protocol instance of the \(\DBSprove\leftrightarrow \DBSverify\) 
    protocol instantiating \(\PK[\alpha][A = g^\alpha]\).
    Each transmission (arrow in the diagram) uses \(\UWBPR\).
    The protocol should be repeated in full to achieve the desired soundness 
    and distance-bounding errors.
  }%
  \label{SchnorrFigure}
\end{figure*}

During one round, in the setup phase, the prover commits to a random nonce: 
more precisely he chooses \(\rho\rgets \ZZ_q\) uniformly at random, computes 
\(R\gets g^\rho\) and sends \(R\) to the verifier.
The verifier generates two challenges \(c_0\rgets \bin^k, c_1\rgets \bin^k\) and sends them to the prover.
The prover computes \(s_0\gets \rho - c_0\alpha, s_1\gets \rho - c_1\alpha\).
This step is the main difference to the original Schnorr protocol: the verifier selects two challenges and the prover computes two responses --- but still only \emph{one nonce}, \(\rho\).
This is also different from the original Brands-Chaum protocol, in which the 
prover and verifier jointly construct \emph{one} challenge with \emph{one} 
response.

In the \ac{DB} phase, the prover notifies the verifier that he has computed 
\(s_0, s_1\).
The verifier chooses one bit, \(b\), uniformly randomly and sends it as a 
challenge to the prover and starts measuring the time of flight.
The prover replies with \(s_b\).
The verifier stops the measurement and verifies that \(R = g^{s_b}A^{c_b}\).

@@

The prover must know the responses for both challenges to successfully pass the \ac{DB} phase.
The reason for having two challenges but only one random nonce is that knowing 
the responses to both means learning \(\alpha\).
This gives us the incentives that prevent \ac{DBTF}.
Bundling the authentication into the distance-bounding phase (difference from 
Brands-Chaum) prevents \ac{DBDH}, and both adaptations together aim at 
\ac{DBMF} resistance.
We do not consider \ac{DBDF} here; since the prover knows the key~\(\sk\), she 
can do \iac{DBEDLC} attack to reduce the distance.
(We will solve this problem in the next section.)

The intuition behind the protocol security is as follows.
To achieve malicious-verifier zero-knowledge, choose \(k\) logarithmic in the 
security parameter \(\lambda\) and repeat the protocol \(n\) times, such that 
the soundness error, \(2^{-kn}\), becomes small enough.
(Repeating the protocol is also needed to decrease the success probability of 
some of adversaries presented below.)

@@

The protocol is also secure against distance hijacking due to the fact that the 
authenticating bitstring is used during the \ac{DB} phase, not the challenge 
bitstring, as is the case for the original protocol of Brands-Chaum.
Thus the probability of success is equivalent of a collision for the responses 
for the chosen challenge --- in each round.

Finally, it follows from the original Schnorr protocol that this is still 
\ac{ZK} and \iac{PK} with soundness error \(2^{-kn}\).
\daniel{I should prove this for the composed protocol, I should check the details with Douglas.}

>>>>

\section{Distance-bounding \aclp*{ZKPK} for discrete logarithms}%
\label{DB-anon-cred}

@@

    \(s_1\gets \rho - c_1\alpha \pmod q\)
    & \(\ProtoSendLeft{c_1, \dotsc, c_k}\)
    & \(c_1\rgets \bin^k, \dotsc, c_k\rgets \bin^k\)
    \\

    \vdots
    &
    &
    \\[-1em]

    \(s_k\gets \rho - c_k\alpha \pmod q\)
    &
    &
    \\

@@

    % null
    & \(\ProtoSendLeft{i}\)
    & \(i\rgets \{1, \dotsc, k\}\), start clock
    \\

    Fetch \(s_i\)
    & \(\ProtoSendRight{s_i}\)
    & Stop clock, record \(\Delta t\)
    \\

@@

    % null
    &
    & Accept if \(R = g^{s_i} A^{c_i}\) and \(\Delta t < t_{\max}\).
    \\

  \end{tabular}
  \caption{%
    One-round protocol instance of the \(\DBSprove\leftrightarrow \DBSverify\) 
    protocol instantiating \(\PK[\alpha][A = g^\alpha]\).
    Each transmission (arrow in the diagram) uses \(\UWBPR\).
    The protocol should be repeated \(n\) times to achieve the desired 
    soundness and distance-bounding errors.
  }%
  \label{SchnorrFigure}
\end{figure*}

During one round, in the setup phase, the prover commits to a random nonce: 
more precisely he chooses \(\rho\rgets \ZZ_q\) uniformly at random, computes 
\(R\gets g^\rho\) and sends \(R\) to the verifier.
The verifier generates \(k\) challenges \(c_1\rgets \bin^k, \dotsc, c_k\rgets 
  \bin^k\) (bit strings of length \(k\)) and sends them to the prover.
The prover computes one response per challenge, \(s_1\gets \rho - c_1\alpha, 
  \dotsc, s_k\gets \rho - c_k\alpha\).
This step is the main difference to the original Schnorr protocol: the verifier 
selects several challenges and the prover computes several responses --- but 
still only use \emph{one nonce}, \(\rho\).
This is needed for \ac{DBTF} resistance.
This is also different from the original Brands-Chaum protocol, in which the 
prover and verifier jointly construct \emph{one} challenge with \emph{one} 
response.

In the \ac{DB} phase, the prover notifies the verifier that he has computed 
\(s_1, \dotsc, s_k\).
The verifier chooses one of the challenges, \(i\), uniformly randomly and sends 
it as a challenge to the prover and starts measuring the time of flight.
The prover replies with \(s_i\).
The verifier stops the measurement and verifies that \(R = g^{s_i}A^{c_i}\) and 
that the time of flight was within \(t_{\max}\) (determined from the allowed 
  distance).

@@

The intuition behind the protocol security is as follows.
The prover must know the responses for all challenges to successfully pass the 
\ac{DB} phase.
The reason for having several challenges but only one random nonce is that 
knowing at least two responses means learning \(\alpha\).
This gives us the incentives that prevent \ac{DBTF}.
Bundling the authentication into the distance-bounding phase (difference from 
Brands-Chaum) prevents \ac{DBDH}.
We do not consider \ac{DBDF} here; since the prover knows the key~\(\sk\), she 
can do \iac{DBEDLC} attack to reduce the distance.
(We will solve this problem in the next section.)
However, the properties of \(\UWBPR\) ensures \ac{DBMF} resistance.

@@

The protocol is also secure against distance hijacking due to the fact that the 
authenticating bit string is used during the \ac{DB} phase, not the challenge 
bit string, as is the case for the original protocol of Brands-Chaum.
Thus the probability of success is equivalent of a collision for the responses 
for the chosen challenge --- in each round.

\Ac{DBDH} requires that the adversary finds a collision between his response 
and that of the honest prover.
\dots

Finally, it follows from the original Schnorr protocol that this is still 
\ac{ZK} and \iac{PK} with soundness error \(2^{-kn}\).
To achieve malicious-verifier zero-knowledge, choose \(k\) logarithmic in the 
security parameter \(\lambda\) and repeat the protocol \(n\) times.

\daniel{I should prove this for the composed protocol, I should check the details with Douglas.}
